Using Refactoring Techniques to Reduce Duplication in Object-Oriented Programming Languages\\- Work in Progress -

### 2019-04-29 sattose/paper.tex
Merging chapter

The most trivial way to merge a clone is though method extraction. However, method extraction is not always possible. For instance, if a part of a subtree (in a programs' AST) is matched as a clone. Because of this, we chose to measure what percentage of ``Partial Method'' clones are refactorable using method extraction. Our results are displayed in figure

%TODO: Show and discuss measurements

@@

\section{Conclusion and next steps}
We conclude that most clones are found in methods, but no easy refactoring is available for them. Most clones have complex nesting, and need further consideration to be able to merge them. The study that we have conducted so far analyzes different kinds of clones for harmfulness and prioritizes their refactoring. On basis of this we will extend our tool, CloneRefactor, to be able to apply refactorings to the found clones. We will formalize refactorings for clones that make use of their relation. We found that almost 40\% of the clones are unrelated, so we will start formalizing refactorings by finding a refactoring opportunity for such clones.

%TODO: Expand conclusion

>>>>

The most trivial way to merge a clone is though method extraction. However, method extraction is not always possible. For instance, if a part of a subtree (in a programs' AST) is matched as a clone. Because of this, we chose to measure what percentage of ``Partial Method'' clones are refactorable using method extraction. Our results are displayed in table \ref{table:refactorability}.

\begin{table}[H]
  \begin{center}
  \caption{Clone instance contents} \label{table:refactorability}
  \bigskip
\begin{tabular}{|l|l|l|}
\hline
\textbf{Refactorability}        & \textbf{Amount} & \textbf{Percentage} \\ \hline
Cannot directly be extracted    & 10990           & 41,91               \\ \hline
Can be extracted                & 5791            & 22,08               \\ \hline
Not possible because of content & 9444            & 36,01               \\ \hline
\end{tabular}
\end{center}
\end{table}

From this table we can see that approximately 22 percent of the clones can be refactored through method extraction. For the other clones, we must first build a catalog of appropriate refactorings.

@@

\section{Conclusion and next steps}
We conclude that most clones are found in methods, but most cannot be refactored using only method extraction (as is often assumed when dealing with duplication in code). Most clones have complex nesting, and need further consideration to be able to merge them. The study that we have conducted so far analyzes the context of different kinds of clones and prioritizes their refactoring. On basis of this we will extend our tool, CloneRefactor, to be able to apply refactorings to the found clones.
